---
title: "Workflow for R with TargetHub"
author: "Trung and Camilla"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r include=FALSE}
library(miRNAtargetpackage)
library(jsonlite)
library(httr)
```

### General information for the miRNAtargetpackage
The database targetHub contains information about different kinds of transcripts of genes (genes inside our cells in teh body are responsible for how people look like etc.). messengerRNNA (=mRNA) are transcribed from genes as well as microRNA (=miRNA). miRNA can appear in two forms: spem-loop miRNA and mature miRNA. With the miRNAtargetpackage one can retreive information from targetHub about which genes (=mRNA) that can interact with specific miRNAs and vicer versa. 

It is possible to send three different kinds of requests to targetHub:

1)	Either you have a name of a gene (= the mRNA name) (input)  and you want a list of the miRNAs that are associated with that gene (=miRNA-target interactions) (output).

2)	Or you have a name of a miRNA-variant of stem-loop type (input) and you want a list of the miRNAs that can bind to the stem-loop miRNA (output).

3)	Or you have a name of a miRNA-variant of mature type (input) and you want a list of the miRNAs that can bind to the mature miRNA (output).

In the output there is a list of miRNA-target interactions.


### 1. Query by gene

miRNA-target interactions of Entrez Gene \"672\" (BRCA1) that are supported by **atleast** three data sources/methods.


```{r}
miRNA_target_interactions("gene", "evidence count", 672,  3, TRUE)
# Gene
	print('1-------------------')
	r = miRNA_target_interactions("gene", "evidence count", 672,  3, TRUE)
	print(r$url)
	print(head(as.list(r)))

	print('2-------------------')
	r = miRNA_target_interactions("gene", "specific method", 672,  3, TRUE)
	print(r$url)
	print(head(as.list(r)))

	
```


miRNA-target interactions of Entrez Gene \"672\" (BRCA1) that are supported by **miRTarBase**

```{r}
	r = miRNA_target_interactions("gene", "specific method", 672,  "mirtarbase", TRUE)
	print(r$url)
	print(head(as.list(r)))

	print('4-------------------')
	r = miRNA_target_interactions("gene", "specific method", 672,  "mirtarbase", FALSE)
	print(r$url)
	print(head(as.list(r)))

```

### 2. Query by stem-loop miRNA

miRNA-target interactions of miRNA \"hsa-mir-212\" that are supported by **atleast** four data sources/methods

```{r}
print('5-------------------')
	r = miRNA_target_interactions("stem-loop miRNA", "evidence count", "hsa-mir-212",  4)
	print(r$url)
	print(head(as.list(r)))

	print('6-------------------')
	r = miRNA_target_interactions("stem-loop miRNA", "evidence count", "hsa-mir-212",  4, TRUE)
	print(r$url)
	print(head(as.list(r)))
```

miRNA-target interactions of miRNA \"hsa-mir-212\" that are supported by _PicTar (5)__

```{r}
print('7-------------------')
	r = miRNA_target_interactions("stem-loop miRNA", "specific method", "hsa-mir-212", "pictar5")
	print(r$url)
	print(head(as.list(r)))
```

miRNA-target interactions of miRNA \"hsa-mir-212\" that are supported by four methods _miRanda, miRTarBase, PicTar (4)and TargetScan_

```{r}
print('8-------------------')
	r = miRNA_target_interactions("stem-loop miRNA", "specific method", "hsa-mir-212", "miranda+mirtarbase+pictar4+targetscan", TRUE)
	print(r$url)
	print(head(as.list(r)))
```

### 3. Query by mature miRNA

miRNA-target interactions of mature miRNA \"hsa-miR-212-3p\" (stem-loop: hsa-mir-212) that are supported by **atleast** four data sources/methods

```{r}
print('9-------------------')
	r = miRNA_target_interactions("mature miRNA", "evidence count", "hsa-miR-212-3p",  4)
	print(r$url)
	print(head(as.list(r)))

	print('10-------------------')
	r = miRNA_target_interactions("mature miRNA", "evidence count", "hsa-miR-212-3p",  4, TRUE)
	print(r$url)
	print(head(as.list(r)))
```

miRNA-target interactions of mature miRNA \"hsa-miR-212-3p\" (stem-loop: hsa-mir-212) that are supported by _TargetScan_

```{r}
print('11-------------------')
	r = miRNA_target_interactions("mature miRNA", "specific method", "hsa-miR-212-3p", "targetscan")
	print(r$url)
	print(head(as.list(r)))
```

miRNA-target interactions of mature miRNA \"hsa-miR-212-3p\" (stem-loop: hsa-mir-212) that are supported by two methods _miRanda and TargetScan_

```{r}
print('12-------------------')
	r = miRNA_target_interactions("mature miRNA", "specific method", "hsa-miR-212-3p", "miranda+targetscan", TRUE)
	print(r$url)
	print(head(as.list(r)))
```
