---
title: "Workflow for R with TargetHub"
author: "Trung and Camilia"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r}
library(miRNAtargetpackage)
library(jsonlite)
library(httr)
```

### 1. Query by gene

miRNA-target interactions of Entrez Gene \"672\" (BRCA1) that are supported by **exactly** three data sources/methods

```{r}
tmp = miRNA_target_interactions("gene", "evidence count", 672,  3)
print(tmp$extract())
print(jsonlite::toJSON(tmp$extract()))
```

miRNA-target interactions of Entrez Gene \"672\" (BRCA1) that are supported by **atleast** three data sources/methods

```{r}
print(tmp$atleast())
print(jsonlite::toJSON(tmp$atleast()))
```

miRNA-target interactions of Entrez Gene \"672\" (BRCA1) that are supported by **miRTarBase**

```{r}
tmp = miRNA_target_interactions("gene", "specific method", 672,  "mirtarbase")
print(tmp$extract())
print(jsonlite::toJSON(tmp$extract()))
```
_Note_: only extract method available for database as data source.

miRNA-target interactions of Entrez Gene \"672\" (BRCA1) that are supported by **three** methods _miRanda, PicTar and TargetScan_

```{r}
tmp = miRNA_target_interactions("gene", "specific method", 672,  "miranda+pictar4+targetscan")
print(tmp$extract())
print(jsonlite::toJSON(tmp$extract()))
```

### 2. Query by stem-loop miRNA

miRNA-target interactions of miRNA \"hsa-mir-212\" that are supported by **exactly** four data sources/methods

```{r}
tmp = miRNA_target_interactions("stem-loop miRNA", "evidence count", "hsa-mir-212",  4)
print(tmp$extract())
print(jsonlite::toJSON(tmp$extract()))
```

miRNA-target interactions of miRNA \"hsa-mir-212\" that are supported by **atleast** three data sources/methods

```{r}
print(tmp$atleast())
print(jsonlite::toJSON(tmp$atleast()))
```

miRNA-target interactions of miRNA \"hsa-mir-212\" that are supported by _PicTar (5)__

```{r}
tmp = miRNA_target_interactions("stem-loop miRNA", "specific method", "hsa-mir-212",  "pictar5")
print(tmp$extract())
print(jsonlite::toJSON(tmp$extract()))
```
_Note_: only extract method available for database as data source.

miRNA-target interactions of miRNA \"hsa-mir-212\" that are supported by four methods _miRanda, miRTarBase, PicTar (4)and TargetScan_

```{r}
tmp = miRNA_target_interactions("stem-loop miRNA", "specific method", "hsa-mir-212",  "miranda+mirtarbase+pictar4+targetscan")
print(tmp$extract())
print(jsonlite::toJSON(tmp$extract()))
```

### 3. Query by mature miRNA

Evidence Count	miRNA-target interactions of mature miRNA \"hsa-miR-212-3p\" (stem-loop: hsa-mir-212) that are supported by **exactly** four data sources/methods

```{r}
tmp = miRNA_target_interactions("mature miRNA", "evidence count", "hsa-miR-212-3p",  4)
print(tmp$extract())
print(jsonlite::toJSON(tmp$extract()))
```

miRNA-target interactions of mature miRNA \"hsa-miR-212-3p\" (stem-loop: hsa-mir-212) that are supported by **atleast** four data sources/methods

```{r}
print(tmp$extract())
print(jsonlite::toJSON(tmp$extract()))
```

miRNA-target interactions of mature miRNA \"hsa-miR-212-3p\" (stem-loop: hsa-mir-212) that are supported by _TargetScan_

```{r}
tmp = miRNA_target_interactions("mature miRNA", "specific method", "hsa-mir-212-3p",  "targetscan")
print(tmp$extract())
print(jsonlite::toJSON(tmp$extract()))
```
_Note_: only extract method available for database as data source.

miRNA-target interactions of mature miRNA \"hsa-miR-212-3p\" (stem-loop: hsa-mir-212) that are supported by two methods _miRanda and TargetScan_

```{r}
tmp = miRNA_target_interactions("mature miRNA", "specific method", "hsa-miR-212-3p",  "miranda+targetscan")
print(tmp$extract())
print(jsonlite::toJSON(tmp$extract()))
```
